\documentclass[a4paper]{arthur-letter}

\title{Citibank Group, Inc. Engages in Fascism and Nation State Level Hacking of Ex US Navy SEAL Matthew Woods.}

\author{Matthew Woods F.K.A. Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods F.K.A. Burns}            % Your full name
\linkedin{/in/matthew-woods-75bb721a5}       % Your linkedin
\mail{mattwoods243@outlook.com}       % Your email
\numberphone{+1 808 445 9723}                % Your phone number
\lettitle{Citigroup, Inc. and Wells Fargo participate in fascism and nation state level hacking against a struggling disabled Navy SEAL startup: XignalX, Inc.} % Title of your letter
\site{mattwoods5326.wixsite.com/xignalxincformerlyxi}                       % Your site
\github{XmattwoodsX}
\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA, 94042}

    \begin{letter}

    \subject{TLDR: I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc. while working as a Google employee. From 2015-2020, I have experienced severe police misconduct first hand. This is across five counties: San Diego, Orange, Santa Clara, Oahu and Hawaii. I think they may have ties to THE Nazis, since my entire immediate family (Donald Burns, Anne Burns and Susan Burns) are Nazis... the type that agree with Adolf Hitler and Eichmann of WWII. They lied to me about this since I was born. Target Corporation, local strip malls and police succumb to fascism and try to suppress me in all ways. on top of that, Citigroup Inc. and Wells Fargo launch denial of service attacks to me and XignalX Inc: a struggling startup owned by disabled former US Navy SEALs in Hawaii. Nation state level hacking is apparent.
}
            
    URGENT UPDATE RE Citibank and Wells Fargo
            
    \opening{Dear New York Times,}
            
    From my original letter, "Alphabet Inc. Lies, Blacklists and Conspiracy" \cite{alphabetinc}:

    This is the second attack by Citigroup Inc on XignalX Inc... Both in broad daylight. The first time, I was in Oakland, CA authoring a letter to the New York Times \cite{alphabetinc}. They hacked, on my then iphone, the Citigroup iOS app, web app, the call center, and, indeed, in person at a branch in Oakland. During the previous episode, the teller at the Citi branch (4101 Piedmont Ave, Oakland, CA 94611) told me the amount of my balance, then immediately got locked out of control from their system. They WOULD NOT GIVE ME MY MONEY... DESPITE ME PROVIDING PROPER ID AT THE SCENE. THEY WOULD NOT RELEASE MY FUNDS. This is a direct connection to the Nazi network that seems to be operating with impunity in America right now, as well as Trump and his network.

    This recent episode is identical. They are doing a repeat of the first attack, but this time I have no ID, a prepaid cell phone and the debit card. They are lying... Just as wells Fargo did back in 2019, when I quit Alphabet Inc. They are doing everything in their power to hack my finances to prevent me from speaking out. It is oppression, by the Nazis, wrt my family and the situation I described in the earlier letter. I advised Citigroup Inc over the phone of impending legal action and the Nazi operative told me that I was warned to shut up. Then they informed me that they would not unblock the card and went dead silent on the other end... As if to give me one final FUCK YOU right to my face. As if they are above the law. I want Citigroup to wind down. They THINK they are "too big to fail"... I BEG TO DISAGREE. 

    I sit at the big island Hawaii now, under relentless attack from industry and state. They won't stop harassing me because I am speaking out. I must conclude that they are part of the Nazi movement and are cooperating with Alphabet Inc. to disrupt the activities of XignalX, Inc. Barbaric and cruel for a former SEAL owned startup. 

    I have been locked out of all my normal email accounts because my Titan key was stolen (along with my last meager possessions such as a tent and backpack and Last Will and Testament/Advance Directive. They obviously think they are going to murder me before anyone finds out. The police even joke about that point right in front of my face... Murdering/torturing me. Someone please call these assholes out for Trump's fascist control over the US government/military industrial complex. They have LITERALLY LOCKED ME OUT OF MY CHECKING ACCOUNT ILLEGALLY. THEY ARE NAZIS. FULL STOP \cite{{targetcorporationhitlersalute} \cite{bigbangtheoryhouse5058pendleton} \cite{stripmalls}.
            
            \closing{Yours sincerely,} % To adapt following recipient

            \signing{Matthew Woods (F.K.A. Burns)}

    \end{letter}
    
\begin{thebibliography}{}

\bibitem{alphabetinc}
Alphabet, Inc, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:8016c2b0-e71f-4c2c-995d-b67174459387

p\bibitem{targetcorporationhitlersalute}
Target Corporation, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:f7522e8c-d944-449d-8fbd-f68dd59e60cb

\bibitem{bigbangtheoryhouse5058pendleton}
Big Bang Theory House (ft The Physics Girl), http://courtindex.sdcourt.ca.gov/CISPublic/casedetail?casenum= DV041758\&casesite=SD\&applcode=D

\bibitem{stripmalls}
Strip Malls, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:83be49a8-3869-4166-9204-21ff644ca4ac

\end{thebibliography}
\end{document}